Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-09-20 paper/referee_response.txt

	--suggestion for going a bit deeper in Sec 5.1: some surveys may find
	  it difficult to rotate their hardware randomly with every shot.
	  Could you do a survey E which has random pointing centers but no
	  rotation?

The referee is absolutely right that there are cameras that cannot be rotated with respect to the sky. That is one of the reasons why we designed Survey C without rotation. Since Survey C calibrates just as well as Survey D, we conclude that rotation is not necessary for good self-calibration. We agree that a Survey E would confirm that, but we believe that Survey C already makes this point well. We added a few sentences to the discussion of Survey C and D about this point in Sections 5.1 and 5.2.

	--suggestion for going a bit deeper in Sec 5.2 (and/or Sec 4): you
	  show the residuals in the instrument response, but more relevant
	  might be the residuals in the final survey.  For Survey A (and to a
	  large extent B), the residuals in the final survey are just as bad
	  as in the instrument response.  But in Surveys C and D, they get beat
	  down because the calibration error on a given piece of sky changes
	  from observation to observation.  It would be instructive to add a
	  performance metric which includes this effect.

This is an excellent suggestion. We have added Figures 7 to 11, which show the residuals in the final survey. We comment on these figures in Section 5.2, and we feel that this led to a substantial improvement of the paper.

In Addition to these changes, we also made the following small changes:
	- We removed "Large-Scale" from the paper title
	- We corrected a few minor bugs in the code, none of which made made significant changes to the contents of the paper.
	- We have modified the form of the true instrument response (last equation in 2.2.3) to now include a (1+a+b)**-0.5 factor. This reduces the magnitude of the high frequency sine and cosine contributions. We did this so that the best-in-basis instrument response was closer to the true instrument response. 
	- The code used in this work is publicly available and we added the github links in Section 2 and the Acknowledgements 
	- We re-ran the simulations with a higher source density (d = 300 not d = 100 deg^-2), as this makes the survey residual plots (Figure 7 - 11) clearer.
	- For clarity, we have slightly reworded the abstract.
	- Finally, we have also corrected a few typos.

### 2012-09-20 paper/self_calibration_I.tex
increase strength of sine and cosines so that see difference better between B and C

\subsubsection{True Instrument Response Model}
\label{sec:instrument_response_model}
We construct a complex, position independent instrument response model $f_\true(\vec{x_i} | \vec{q}_{\true})$ from a superposition of large- and small-scale variations:
\begin{eqnarray*}
f_\true(\vec{x_i} | \vec{q}_{\true, 1 \ldots 260}) = f_\text{large}(\vec{x_i} | \vec{q}_{\true, 1 \ldots 6}) + f_\text{small}(\vec{x_i} | \vec{q}_{\true, 7 \ldots 260}) \quad ,
\end{eqnarray*}
where $\vec{x_i} = (x_i, y_i)$ is the focal-plane position that the $k$th source falls at during the $i\text{th}$ measurement and $\vec{q}_\true$ are the parameters defining the instrument response model. This response model subsumes various effects commonly discussed in terms of detector flat-fielding and optical vignetting. The large-scale instrument response $f_\text{large}(\vec{x_i} | \vec{q}_{\true, 1 \ldots 6})$ is modeled as a second order polynomial:
\begin{eqnarray*}
f_\text{large}(\vec{x_i} | \vec{q}_{\true, 1 \ldots 6}) = q_{\true, 1} + q_{\true, 2} \, x_i + q_{\true, 3} \, y_i + q_{\true, 4} \, x_i^2 + q_{\true, 5} \, x_i \, y_i  + q_{\true, 6} \, y_i^2  \quad .
\end{eqnarray*}
The small-scale instrument response, which is constructed from sine and cosine contributions, is superimposed on this large-scale instrument response. The small-scale instrument response $f_\text{small}(\vec{x_i} | \vec{q}_{\true, 7 \ldots 260})$ is modeled as
\begin{eqnarray*}
f_\text{small}(\vec{x_i} | \vec{q}_{\true, 7\ldots 260})  & = &  \sum_{a=0}^6 \sum_{b=0}^a \left(1 + a + b\right) ^ {-0.5} \left[ q_{\true, 7+4b} \cos (k_x \, x_i) + q_{\true, 8+4b} \sin (k_x \, x_i) \right] \\
& & \qquad \qquad \times \left[ q_{\true, 9+4b} \cos (k_y \, y_i) + q_{\true, 10+4b} \sin (k_y \, y_i) \right] \quad ,
\end{eqnarray*}
where
\begin{eqnarray*}
k_x & = & \dfrac{a \, \pi}{X} \quad ,\\
k_y & = & \dfrac{b \, \pi}{Y} \quad ,\\
\end{eqnarray*}
with the physical focal-plane dimensions $X$ and $Y$. The $(1 + a +d)^{-0.5}$ factor reduces the magnitude of the higher order terms. In total, the instrument response model is parameterized with 260 parameters; an example can be seen in Figure \ref{fig:single_image} (right). It is this instrument response that we try and recover with the self-calibration procedure. With this instrument response model, we have assumed that the variations in sensitivities on a pixel-to-pixel-scale have been calibrated with some other method, such as an internal flat-field calibration source. It is only the variations on larger scales that we aim to constrain with the self-calibration procedure. Our final assumption in these simulations is that the instrument response is temporally stable.

@@

Ultimately, survey design requires trade-offs between calibration
requirements and other requirements related to cadence, telescope
overheads, and observing constraints (like alt, az, airmass, and
field-rotation constraints).  One requirement that is often
over-emphasized, however, is conceptual or apparent ``uniformity'';
these different survey strategies have different uniformities of
coverage, each with possibly non-obvious consequences.  Many
astronomers will see survey strategy A as being ``more uniform'' in
its coverage (especially relative to survey D).  This is not true, if
uniformity is defined by the variance or skewness or any other simple
statistic in exposure times; strategy D is extremely uniform (more
uniform than Poisson, for example).  In any survey, past and future,
variations in exposure time have been valuable for checking systematic
and random errors, and don't---in themselves---make it difficult to
obtain a uniform survey in properties like brightness (since samples
can be cut on any well-measured property).  In general, in the
presence of real astronomical variations in distributions of
luminosity, distance, metallicity, and (more importantly) extinction
by dust, there is no way to make a survey uniformly sensitive to the
objects of interest.  As a community we should be prepared to adjust
our analysis for the non-uniformity of the survey rather than adjust
(cut) our data to match the uniformity of unrealistically simplified
analyses.  This is already standard practice in the precise
cosmological measurement experiments, and will be required practice
for the next generation of massively-multiple-epoch imaging surveys.

>>>>

\subsubsection{True Instrument Response Model}
\label{sec:instrument_response_model}
We construct a complex, position independent instrument response model $f_\true(\vec{x_i} | \vec{q}_{\true})$ from a superposition of large- and small-scale variations:
\begin{eqnarray*}
f_\true(\vec{x_i} | \vec{q}_{\true, 1 \ldots 260}) = f_\text{large}(\vec{x_i} | \vec{q}_{\true, 1 \ldots 6}) + f_\text{small}(\vec{x_i} | \vec{q}_{\true, 7 \ldots 260}) \quad ,
\end{eqnarray*}
where $\vec{x_i} = (x_i, y_i)$ is the focal-plane position that the $k$th source falls at during the $i\text{th}$ measurement and $\vec{q}_\true$ are the parameters defining the instrument response model. This response model subsumes various effects commonly discussed in terms of detector flat-fielding and optical vignetting. The large-scale instrument response $f_\text{large}(\vec{x_i} | \vec{q}_{\true, 1 \ldots 6})$ is modeled as a second order polynomial:
\begin{eqnarray*}
f_\text{large}(\vec{x_i} | \vec{q}_{\true, 1 \ldots 6}) = q_{\true, 1} + q_{\true, 2} \, x_i + q_{\true, 3} \, y_i + q_{\true, 4} \, x_i^2 + q_{\true, 5} \, x_i \, y_i  + q_{\true, 6} \, y_i^2  \quad .
\end{eqnarray*}
The small-scale instrument response, which is constructed from sine and cosine contributions, is superimposed on this large-scale instrument response. The small-scale instrument response $f_\text{small}(\vec{x_i} | \vec{q}_{\true, 7 \ldots 260})$ is modeled as
\begin{eqnarray*}
f_\text{small}(\vec{x_i} | \vec{q}_{\true, 7\ldots 260})  & = &  \sum_{a=0}^6 \sum_{b=0}^a \left(1 + a + b\right) ^ {-0.25} \left[ q_{\true, 7+4b} \cos (k_x \, x_i) + q_{\true, 8+4b} \sin (k_x \, x_i) \right] \\
& & \qquad \qquad \times \left[ q_{\true, 9+4b} \cos (k_y \, y_i) + q_{\true, 10+4b} \sin (k_y \, y_i) \right] \quad ,
\end{eqnarray*}
where
\begin{eqnarray*}
k_x & = & \dfrac{a \, \pi}{X} \quad ,\\
k_y & = & \dfrac{b \, \pi}{Y} \quad ,\\
\end{eqnarray*}
with the physical focal-plane dimensions $X$ and $Y$. The $(1 + a +d)^{-0.25}$ factor reduces the magnitude of the higher order terms. In total, the instrument response model is parameterized with 260 parameters; an example can be seen in Figure \ref{fig:single_image} (right). It is this instrument response that we try and recover with the self-calibration procedure. With this instrument response model, we have assumed that the variations in sensitivities on a pixel-to-pixel-scale have been calibrated with some other method, such as an internal flat-field calibration source. It is only the variations on larger scales that we aim to constrain with the self-calibration procedure. Our final assumption in these simulations is that the instrument response is temporally stable.

@@

Ultimately, survey design requires trade-offs between calibration
requirements and other requirements related to cadence, telescope
overheads, and observing constraints (like alt, az, airmass, and
field-rotation constraints).  One requirement that is often
over-emphasized, however, is conceptual or apparent ``uniformity'';
these different survey strategies have different uniformities of
coverage, each with possibly non-obvious consequences.  Many
astronomers will see survey strategy A as being ``more uniform'' in
its coverage (especially relative to strategy D).  This is not true, if
uniformity is defined by the variance or skewness or any other simple
statistic in exposure times; strategy D is extremely uniform (more
uniform than Poisson, for example).  In any survey, past and future,
variations in exposure time have been valuable for checking systematic
and random errors, and don't---in themselves---make it difficult to
obtain a uniform survey in properties like brightness (since samples
can be cut on any well-measured property).  In general, in the
presence of real astronomical variations in distributions of
luminosity, distance, metallicity, and (more importantly) extinction
by dust, there is no way to make a survey uniformly sensitive to the
objects of interest.  As a community we should be prepared to adjust
our analysis for the non-uniformity of the survey rather than adjust
(cut) our data to match the uniformity of unrealistically simplified
analyses.  This is already standard practice in the precise
cosmological measurement experiments, and will be required practice
for the next generation of massively-multiple-epoch imaging surveys.
